Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation

### 2022-11-23 beap_pres_dec2022/beap_pres_dec.tex
Nov 23 - Fixed Brians Edits on literature review/proposal, continued working on beap pres
Nov 23 Updates to beap presentation

	% SLIDE 4 - I do Not Know if I am including this slide
	% The Graphic for this slide is an  
	\begin{frame}{Information and Entropy Content - MAYBE }

@@

	%Slide 12 - Here put the ABC-MCMC algorithm described by Marjoram (one Brian used in his MCMC slides)
	\begin{frame}{ABC-MCMC Algorithm}

@@

>>>>

	% SLIDE 4 - I do Not Know if I am including this slide
	% The Graphic for this slide is an  
	% Entropy, which is measured by Shannon's Entropy equation is a measure of compositional complexity which uses the proportion of residue(s)
	% in a subsequence to measure the compositional state of that subseequence - A lower variety of residues = lower entropy 
	\begin{frame}{Shannon's Entropy - MAYBE }

			$H = -L\sum p_i log_2(p_i)$

@@

	%Slide 12 - Here put the ABC-MCMC algorithm described by Marjoram (one Brian used in his MCMC slides)
	\begin{frame}{MCMC for ABC}

		\begin{enumerate}
			\item Propose a move from $\theta$ to $\theta'$ according to a transition kernel $q(\theta,\theta')$.
			\item Generate simulated dataset $D'$ using $\theta'$ and calculate $S'$.
			\item If $\rho(S', S) \le \epsilon$ continue to 4, otherwise remain at $\theta$ and go to 1.
			\item Calculate \newline \begin{center}$\alpha(\theta, \theta') = min(1, \frac{\pi(\theta')q(\theta',\theta)}{\pi(\theta)q(\theta, \theta')})$ \end{center}
			\item Accept $\theta'$ with probability $\alpha$, otherwise stay at $\theta$.
			\item Return to 1.
		\end{enumerate}

@@

		\begin{enumerate}
			\item 
			\item
			\item
			\item
			\item
		\end{enumerate}
